Gelation as a condensation frustrated by hydrodynamics and mechanical tension

### 2014-08-22 generate.tex
fig:wholeprocess reduced 3D snapshots, porod and qmax

\begin{figure*}
	\tikzset{external/force remake}
	\tikzsetnextfilename{cell_vs_cap}
	\begin{tikzpicture}[
		pic3d/.style={inner sep=0}, %
		lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries},%
		]%
		%box
		\draw[every node/.style={draw, inner sep=0, minimum width=0.01\textwidth, minimum height=0.12\textwidth, anchor=south west}] 
			node (Rrightwall) at (0, 0) {}
			node (Rleftwall) at (0.2\textwidth, 0) {}
			[every node/.append style={minimum height=0.06\textwidth}]
			node (Crightwall) at (0, 0.13\textwidth) {}
			node (Cleftwall) at (Crightwall.south -| Rleftwall.west) {}
			(Crightwall.north west) +(0,0.005\textwidth) rectangle (Cleftwall.north east);

@@

		\begin{axis}[%
			at={($(cellsketch.north west)+(\textwidth,0)$)}, anchor=outer north east,%
			name={phasediag},%
			width=0.425\textwidth, height=0.3\textwidth,%
			xmin=0, xmax=40, xlabel={$\phi$}, x unit={\%},
			ymin=0.08, ymax=3.5, ylabel={$c_p$}, y unit={\si{\gram\per\litre}},%
			%ytick={0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,2}, yticklabels={0.1,0.2,,,0.5,,,,,1,2},%
			legend pos=north east,%
			legend style={font=\footnotesize},%
			only marks,%
			]%
			\addplot[sharp plot, no marks] table [x expr=100*\thisrowno{0}, y index=1] {gasliquid_sg.phd};
			%\addplot[sharp plot, no marks, dashed] table [x expr=100*\thisrowno{0}, y index=1] {gasliquid_bg.phd};
			%\addplot[sharp plot, no marks, dotted] table [x expr=100*\thisrowno{0}, y index=1] {fluidsolid_f.phd};
			%\addplot+[forget plot] table [x index=1,y index=2] {phase_diag_capillary.csv};
			\addplot table [x index=1,y index=2] {phase_diag_gel.csv};
			\addplot table [x index=1,y index=2] {phase_diag_fluid.csv};
			\addplot table [x index=1,y index=2] {phase_diag_clusters.csv};
			\legend{spinodal, gel, fluid, clusters};
			\node[circle, draw, gray] at (axis cs:7.4, 0.98) (155C) {};
			\node[draw, gray] at (axis cs:30, 1) (Cap1) {};
		\end{axis}
		\node[lab] at (phasediag.outer north west) {b};
	\end{tikzpicture}
	\caption{\textbf{Reservoir cell} \textbf{a} Sketch of our experimental setup. The observation cell contains initially colloids, polymer and no salt. \textbf{b} Phase diagram. \textbf{c-e} Comparison between gels made at the same state point ($\phi=27~\%$, $c_p=\SI{0.75}{\gram\per\litre}$) either in situ (\textbf{c}, blue) or ex situ (\textbf{d}, red).}
	\label{fig:cell_vs_cap}
\end{figure*}
\end{document}

>>>>

\begin{figure*}
	%\tikzset{external/force remake}
	\tikzsetnextfilename{cell_vs_cap}
	\begin{tikzpicture}[
		pic3d/.style={inner sep=0}, %
		lab/.style={below right, text height=0.8em, text depth=0.2em, font=\Large\bfseries},%
		]%
		%box
		\draw[every node/.style={draw, inner sep=0, minimum width=0.01\textwidth, minimum height=0.12\textwidth, anchor=south west}] 
			node (Rrightwall) at (0, 0) {}
			node (Rleftwall) at (0.2\textwidth, 0) {}
			[every node/.append style={minimum height=0.06\textwidth}]
			node (Crightwall) at (0, 0.13\textwidth) {}
			node (Cleftwall) at (Crightwall.south -| Rleftwall.west) {}
			(Crightwall.north west) +(0,0.005\textwidth) rectangle (Cleftwall.north east);

@@

		\begin{axis}[%
			at={($(cellsketch.north west)+(\textwidth,0)$)}, anchor=outer north east,%
			name={phasediag},%
			width=0.425\textwidth, height=0.3\textwidth,%
			xmin=0, xmax=40, xlabel={$\phi$}, x unit={\%},
			ymin=0.08, ymax=3.5, ylabel={$c_p$}, y unit={\si{\gram\per\litre}},%
			%ytick={0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,2}, yticklabels={0.1,0.2,,,0.5,,,,,1,2},%
			legend pos=north east,%
			legend style={font=\footnotesize},%
			only marks,%
			]%
			\addplot[sharp plot, no marks] table [x expr=100*\thisrowno{0}, y index=1] {gasliquid_sg.phd};
			%\addplot[sharp plot, no marks, dashed] table [x expr=100*\thisrowno{0}, y index=1] {gasliquid_bg.phd};
			%\addplot[sharp plot, no marks, dotted] table [x expr=100*\thisrowno{0}, y index=1] {fluidsolid_f.phd};
			%\addplot+[forget plot] table [x index=1,y index=2] {phase_diag_capillary.csv};
			\addplot table [x index=1,y index=2] {phase_diag_gel.csv};
			\addplot table [x index=1,y index=2] {phase_diag_fluid.csv};
			\addplot table [x index=1,y index=2] {phase_diag_clusters.csv};
			\legend{spinodal, gel, fluid, clusters};
			\node[circle, draw, gray] at (axis cs:7.4, 0.98) (155C) {};
			\node[draw, gray] at (axis cs:30, 1) (Cap1) {};
		\end{axis}
		\node[lab] at (phasediag.outer north west) {b};
	\end{tikzpicture}
	\caption{\textbf{Reservoir cell} \textbf{a} Sketch of our experimental setup. The observation cell contains initially colloids, polymer and no salt. \textbf{b} Phase diagram. \textbf{c-e} Comparison between gels made at the same state point ($\phi=27~\%$, $c_p=\SI{0.75}{\gram\per\litre}$) either in situ (\textbf{c}, blue) or ex situ (\textbf{d}, red).}
	\label{fig:cell_vs_cap}
\end{figure*}

\begin{figure*}
	\tikzset{external/force remake}
	\tikzsetnextfilename{wholeprocess}
	\begin{tikzpicture}
	\begin{groupplot}[
	group style={
			group name=g, group size=1 by 2,
			vertical sep=3em,
			},
		width=0.4\textwidth,%
		height=0.2\textwidth+1em,%
		ylabel absolute, every axis y label/.append style={anchor=base, yshift=-1.5em}
		]
		\nextgroupplot[
			xlabel={time (min)},
			ymin=0, ymax=3, ylabel={Porod exponent},]
		\addplot[no marks, error bars/.cd, y dir=both,y explicit] table[y error index=2] {155C.porod};

		\nextgroupplot[
			xmode=log, ymode=log,
			xlabel={$(t-t_0)/\tau_B$},
			ylabel=$\langle q\rangle\sigma$,
			ytick={0.6,0.8,1,1.6,2}, yticklabels={0.6, 0.8,1,1.6, 2},
			]
		\addplot[only marks] table[x expr=6*(\thisrowno{0}-5)]{155C.qmax};
		\addplot+[red, no marks, domain=50:300] {6*x^(-1/3)} node[midway, above]{$-1/3$};
	\end{groupplot}

	\matrix[
		matrix of nodes, inner sep=0, column sep=0.0125\textwidth, row sep=0.5em,
		matrix anchor=north west,
		at={($(g c1r1.outer north east)+(-\textwidth,0)$)},
		] (m){
		\SI{5}{\minute} & \SI{10}{\minute} & \SI{20}{\minute} \\
		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t024s.png}&
		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t044s.png}&
		\includegraphics[width=0.19\textwidth]{155C_percolation_1645_p2size_t084s.png}\\
		 \SI{30}{\minute} & \SI{40}{\minute} & \SI{50}{\minute}\\
		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t00s.png}&
		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t20s.png}&
		\includegraphics[width=0.19\textwidth]{155C_1715_ageing_p2size_t40s.png}\\
		};

	\end{tikzpicture}
\caption{\textbf{Gelation observed in-situ} in a typical sample ($\phi=7.5~\%$, $c_p=\SI{1}{\gram\per\litre}$). Origin of time is salt introduction. \textbf{a} Reconstruction of experimental coordinates coloured by the number of particles in clusters. \textbf{b} Evolution of Porod exponent. \textbf{c} Growth of the characteristic wave number. Time origin is shifted to correspond to the melting of the Wigner crystal.}
\label{fig:wholeprocess}
\end{figure*}

\end{document}
